Analysis on The COVID-19 Pandemic Disrupted Both School Bullying and Cyberbullying

### 2023-02-21 Outputs/Paper/paper.qmd

We conducted a study to determine if there was a correlation between the increasing anti-Asian sentiment and school bullying in the United States. To do this, we analyzed the correlation between the search frequency for the term "school bullying" and the Asian population of each state. Figures 4 and 5 were used to compare the search frequency of the keyword "school bullying" and the date.

>>>>

Anti-Asian violence skyrocketed over the pandemic. The Center for the Study of Hate and Extremism published a report showing how anti-Asian hate crimes grew by 339 percent last year compared to the year before. The racism was fueled by the pandemic, mainly occurring in highly populated urban cities like New York, San Francisco, and Los Angeles. The percentages of Asian hate crimes in New York rose from 30 to 133 and in San Francisco from 9 to 60. American culture pretends Asian Americans face no discrimination or racism. There are countless examples where when the U.S. was faced with an economic downturn, Asian Americans were affected. The 1982 killing of Vincent Chin in Detroit came after the 1980-1982 Detroit recession and The Page Act of 1875, America's first immigration law that banned Chinese women after the Great Panic of 1873. It's safe to assume an economic horror like the pandemic would lead to hate. It was disconcerting reading about the different hate acts that occurred, and it was clear there needed to be culturally appropriate and accessible community safety programs. From the data provided, we decided to clean it, focusing on the states with an Asian population. There has been mainstream media coverage of anti-Asian racism but little effort toward the Asian American Youth. (could be apart of introduction)

As discussed earlier, there has been a significant increase in anti-Asian culture in the United States over the past year. Many may be attributed to the spread of misinformation and xenophobic rhetoric related to the COVID-19 pandemic, which has stoked hatred against Asian communities. Reports show that 81% of Asian adults state violence against them is increasing. Over 3800 hate-related verbal and physical assaults against Asian Americans have been reported during the pandemic.

We conducted a study to determine if there was a correlation between the increasing anti-Asian sentiment and school bullying in the United States. To do this, we analyzed the correlation between the search frequency for the term "school bullying" and the Asian population of each state. Figures 2 and 3 were used to compare the search frequency of the keyword "school bullying" and the date.
